Large Scale Structure Reconstruction with Short-Wavelength Modes

### 2019-10-18 paper/v2.tex
v2

\date{\today}
\begin{abstract}
\noindent \peikai{Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them by measuring perturbations on small scales.} \RC{Should really say instead something about  the fact that large scale modes are difficult to measure because they are sensitive to systematic observational  errors in galaxy surveys - not that they can't be measured.} Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode. This arises physically because the growth of small scale structures varies depending on the large scale environment in which they reside. This induces small scale clustering in real space and an off-diagonal term in the two-point statistics in Fourier space. We can therefore build a quadratic estimator for the large scale field. We demonstrate that this quadratic estimator works well with an N-body simulation test \RC{what do we find? scales? + final speculative sentence about potential of method to do cosmology}. \peikai{We find this quadratic estimator very powerful for reconstructing long-wavelength modes with the $(2.5\,h^{-1}\,\rm Gpc)^3$ simulation. It provides us with a novel way of studying large scale structure and topics related.}

\end{abstract}
\maketitle
\section{Introduction}
Measuring the distribution of structures on large scales has been one of the main goals of recent surveys\peikai{, through which we can have a better constraint of $f_{\rm NL}$ or solve large scale anomalies,} despite it is hard to accomplish directly.\RC{Should include brief examples of why it is very interesting - for example to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting} To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}. The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to fully achieve this goal, we develop in this work a generalized approach of building a quadratic estimator to measure long-wavelength modes indirectly. \\
Starting from second-order standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode. This can be further related to the cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight. Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.\\
The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing. The same statistical feature shows up in our case as well -- the off-diagonal terms of the small scale correlations are no-longer zero, due to the effect of large scale modes. Thus we can create a quadratic estimator for long-wavelength modes using exactly the same formalism. \\
We begin with a brief review of SPT up to second-order in section \ref{sec1}. We then build the quadratic estimator and compute the detectability of the estimator in section \ref{sec2}. In section \ref{sec3} we present a concise study of the estimator with data from N-body simulation. Finally we conclude this work and discuss future work related to this in section \ref{sec4}. We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).

\section{Standard Perturbation Theory}\label{sec1}
In this section we review the SPT approach which describes small scale nonlinearity. \RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter. Stating this explicitly could be helpful for a reader.} \peikai{See also \cite{Bernardeau:2002rev} for a detailed derivation of SPT.} We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit. This non-zero off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator. \\
Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:

@@

&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) \eql{fluid3}

@@

these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.\\
We can solve these equations in Fourier space with perturbative expansion \cite{Bernardeau:2002rev}:

@@

\section{Quadratic Estimator}\label{sec2}
In this section we construct the quadratic estimator for long-wavelength modes starting from \ec{2pt}. We then forecast the detectability of the quadratic estimator for future surveys. As with the case of CMB lensing, we can write the general form of the estimator by averaging over pairs of short-wavelength modes:
\begin{eqnarray}
\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest},
\end{eqnarray} 
with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$  defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
\begin{eqnarray}
A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1} \eql{a}
\end{eqnarray}
In the absence of shot noise the Gaussian noise is given by:
\be 
\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
\ee 
with 
\begin{eqnarray}
&&N(\vec{k}_{l})=2A^2(\vk_{l})\vs
&&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
\end{eqnarray}
where $P_{\rm nl}$ is the nonlinear power spectrum. Minimizing the noise term we can fix the form of $g$ to be:
\begin{eqnarray}
g(\vec{k}_{s},\vec{k}_{s}')=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}
\end{eqnarray} 
The noise term reduces simply to $N(\vk_l)=A(\vk_l)$. We find by testing that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a}, since most of the contribution comes from large $k_s$. We discuss the choice of the upper limit later, in section \ref{sec3}.\\
Assuming Gaussian noise, the projected detectability of a $P(k_l)$ measurement using the quadratic estimator can be expressed as:
\be
\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error},
\ee
where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.\RC{ Write a couple of sentences about Figure 1, bearing in mind that you have put information in the caption already. Also remember to change the survey volume to match DESI and state this.} \peikai{In Fig.~\rf{SN}, we show the projected error of long-wavelength power spectrum using this quadratic estimator with fiducial value $1$. The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$. We will see in the next section \ref{sec3} that this choice of the upper limit is very reasonable for our current construction at $z=0$. Also notice that $P_{\rm lin}(k_l)$ dominates over $N(k_l)$ in \ec{error} for this upper limit, thus the projected error bars are only slightly wider than the cosmic variance error bars ($N=0$ case).}\\
\peikai{plot linear or nonlinear? Change ylabel?}
\Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$. We assume a toy survey of boxsize $L=4\, h^{-1}\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$. Moreover, we set the integration range for $\vk_s$ from $0.03 \,h \,\rm Mpc^{-1}$ to $0.22\,h\,\rm Mpc^{-1}$.}

\section{Demonstration with an N-Body Simulation}\label{sec3}
We test the power of the quadratic estimator using data from a cosmological N-body simulation. We use the $z=0$ snapshot from BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}. The cubical box side length of BigMDPL is $2.5\,h^{-1}\,\rm Gpc$. We use the dark matter particle data to compute the matter density field, leaving the effect of using galaxies or halos to trace the field \cite{Desjacques:2018rev} to  future work.\\ 
We use the code nbodykit \cite{Hand:2018nby} to measure the Fourier density modes, and \ec{quadest} to estimate the long wavelength modes  from the measured short wavelength modes. How well the estimator works can be seen from Fig.~\rf{hist}, where we show histograms of the ratio of the estimated mode amplitudes $\hat{\delta}(\vk_l)$ to their true amplitudes $\delta(\vk_l)$ \peikai{for different values of $\vk_l$}. The two panels show the differences between a short wavelength mode cutoff of $k_s=0.22\, h\, \rm Mpc^{-1}$ and  $k_s=0.37\,h\, \rm Mpc^{-1}$. \peikai{Notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator. As we can see in this plot that individual mode amplitudes are basically unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$. While for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are more biased (the center of the ratio $\sim 20 \%$ too high) and more incorrect (about $\sim 50 \%$ of the modes have negative real parts of $\delta/\hat{\delta}$) due to the increasing inaccuracy of second-order SPT. } \RC{Comment on what the figure shows -  for example individual mode amplitudes are unbiased when $k_s= 0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this here from fig caption: We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are biased (the mode is $\sim 20 \%$ too high) due to the increasing inaccuracy of second-order SPT as we move into nonlinear scales}
\Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}
\\Another goal of this approach is to reproduce large scale structure in real space. To test this, we compute real space density fields by taking the inverse transform of both the directly measured long wavelength Fourier modes and the long wavelength modes predicted using the quadratic estimator. These density fields, $\delta$ and $\hat{\delta}$ respectively are plotted in Fig.~\rf{real}. We can see that \peikai{our quadratic estimator }
\RC{describe how well it works based on what we can see in the figure}
\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row). The bottom row shows their difference. Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.  The upper limit of $\vk_s$ is $0.22 \,h\, \rm Mpc^{-1}$.}

\section{Conclusion}\label{sec4}
In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
\RC{ State that this is good because we won't be sensitive to observational systematics, sky gradients, dust etc}
\RC{Give a short list of cool things we can do, with references: measure 3D clustering beyond the matter radiation equality turnover for the first time, look for evidence of general relativistic effects which are strongest on large scales (e.g., \cite{Jeong:2012ls}), look for evidence of large scale anomalies, like in the CMB, constrain non-Gaussianity,  etc }\\
Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data. The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case. Thus, to detect even larger scales, we may need to use contributions from higher order perturbations and expand the integration range to reduce the noise level. \\
Another issue relates to the range of long-wavelength modes that are detectable. In the N-body simulation,  $k_l$ for modes recovered ranged from $2.5 \,h \times 10^{-3}  \rm Mpc^{-1}$ to $1.3\,h\times 10^{-2}  \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\ 
Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time. As the length scales are so large, a more realistic situation should deal with observations on the light cone. The expression for the quadratic estimator to be generalized to take this into account. Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshifts, in order to include more nonlinear information. Finally, when applied to datasets consisting of halos or galaxies, the approach should be modified to include galaxy bias. We also leave this to future work.\\

\acknowledgements
\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  SD, PL and RC are supported by U.S.\ Dept.\ of Energy contract DE-SC0019248. SD and RC also acknowledge support from NSF AST-1909193.\\
The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu. The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).

>>>>

\date{\today}
\begin{abstract}
\noindent Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them indirectly by observing their impact on small scales perturbations. Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode. This arises physically because small scale structures grow at different rates depending on the large scale environment in which they reside. This induces an off-diagonal term in the two-point statistics in Fourier space that we use as the basis for a quadratic estimator for the large scale field. We demonstrate that this quadratic estimator works well on an N-body simulation of size  $(2.5\,h^{-1}\,\rm Gpc)^3$. In particular, the quadratic estimator successfully reconstructs the long-wavelength modes using only small-scale information. This opens up novel opportunities to study structure on the largest observable scales.

\end{abstract}
\maketitle
\noindent {\it Introduction.}
Measuring the distribution of matter on large scales is one of the goals of cosmological surveys. The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity. %\peikai{, through which we can have a better constraint of $f_{\rm NL}$ or solve large scale anomalies,} despite it is hard to accomplish directly.\RC{Should include brief examples of why it is very interesting - for example to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting} 
Direct measurements are difficult because of systematic effects, so indirect approaches have been considered. Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average. This relation between long- and short-wavelength modes has been discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}. The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to fully achieve this goal, here we construct a quadratic estimator to measure long-wavelength modes indirectly.

Standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop} identifies the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode. Abstractly, this is similar to
cosmic microwave background (CMB) lensing~\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight. Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.
The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing. The same statistical feature shows up in our case as well -- the off-diagonal terms of the small scale correlations are no longer zero, due to the effect of large scale modes. Thus we can create a quadratic estimator for long-wavelength modes using exactly the same formalism.

We begin with a brief review of SPT up to second-order, build the quadratic estimator, and then calculate its detectability. We then apply the estimator to data from a large N-body simulation and demonstrate that it successfully extracts the large scale modes. %Finally we conclude this work and discuss future work related to this in section \ref{sec4}. 
We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014)~\cite{Planck:2014cos} cosmological parameters in this work (to match the parameters of the N-body simulation).

\noindent {\it Standard Perturbation Theory.}\label{sec1}
%In this section we review the SPT approach which describes small scale nonlinearity. \RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter. Stating this explicitly could be helpful for a reader.} \peikai{See also \cite{Bernardeau:2002rev} for a detailed derivation of SPT.} We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit. This non-zero off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator. \\
Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are the continuity, Euler and Poisson equations:

@@

&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) .\eql{fluid3}

@@

These equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.
We can solve these equations perturbatively in Fourier space~\cite{Bernardeau:2002rev}:

@@

\noindent{\it Quadratic Estimator.}\label{sec2}
In this section we construct the quadratic estimator for long-wavelength modes starting from \ec{2pt}. We then forecast the detectability of the quadratic estimator for future surveys. As with the case of CMB lensing, we can write the general form of the estimator by averaging over pairs of short-wavelength modes:
\begin{eqnarray}
\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest},
\end{eqnarray} 
with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$  defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
\begin{eqnarray}
A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1} \eql{a}
\end{eqnarray}
In the absence of shot noise the Gaussian noise is given by:
\be 
\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
\ee 
with 
\begin{eqnarray}
&&N(\vec{k}_{l})=2A^2(\vk_{l})\vs
&&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
\end{eqnarray}
where $P_{\rm nl}$ is the nonlinear power spectrum. Minimizing the noise term we can fix the form of $g$ to be:
\begin{eqnarray}
g(\vec{k}_{s},\vec{k}_{s}')=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}
\end{eqnarray} 
The noise term reduces simply to $N(\vk_l)=A(\vk_l)$. We find by testing that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a}, since most of the contribution comes from large $k_s$. We discuss the choice of the upper limit later, in section \ref{sec3}.\\
Assuming Gaussian noise, the projected detectability of a $P(k_l)$ measurement using the quadratic estimator can be expressed as:
\be
\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error},
\ee
where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.\RC{ Write a couple of sentences about Figure 1, bearing in mind that you have put information in the caption already. Also remember to change the survey volume to match DESI and state this.} \peikai{In Fig.~\rf{SN}, we show the projected error of long-wavelength power spectrum using this quadratic estimator with fiducial value $1$. The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$. We will see in the next section \ref{sec3} that this choice of the upper limit is very reasonable for our current construction at $z=0$. Also notice that $P_{\rm lin}(k_l)$ dominates over $N(k_l)$ in \ec{error} for this upper limit, thus the projected error bars are only slightly wider than the cosmic variance error bars ($N=0$ case).}\\
\peikai{plot linear or nonlinear? Change ylabel?}
\Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$. We assume a toy survey of boxsize $L=4\, h^{-1}\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$. Moreover, we set the integration range for $\vk_s$ from $0.03 \,h \,\rm Mpc^{-1}$ to $0.22\,h\,\rm Mpc^{-1}$.}

\noindent{\it Demonstration with an N-Body Simulation.}\label{sec3}
We test the power of the quadratic estimator using data from a cosmological N-body simulation. We use the $z=0$ snapshot from BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}. The cubical box side length of BigMDPL is $2.5\,h^{-1}\,\rm Gpc$. We use the dark matter particle data to compute the matter density field, leaving the effect of using galaxies or halos to trace the field \cite{Desjacques:2018rev} to  future work.\\ 
We use the code nbodykit \cite{Hand:2018nby} to measure the Fourier density modes, and \ec{quadest} to estimate the long wavelength modes  from the measured short wavelength modes. How well the estimator works can be seen from Fig.~\rf{hist}, where we show histograms of the ratio of the estimated mode amplitudes $\hat{\delta}(\vk_l)$ to their true amplitudes $\delta(\vk_l)$ \peikai{for different values of $\vk_l$}. The two panels show the differences between a short wavelength mode cutoff of $k_s=0.22\, h\, \rm Mpc^{-1}$ and  $k_s=0.37\,h\, \rm Mpc^{-1}$. \peikai{Notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator. As we can see in this plot that individual mode amplitudes are basically unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$. While for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are more biased (the center of the ratio $\sim 20 \%$ too high) and more incorrect (about $\sim 50 \%$ of the modes have negative real parts of $\delta/\hat{\delta}$) due to the increasing inaccuracy of second-order SPT. } \RC{Comment on what the figure shows -  for example individual mode amplitudes are unbiased when $k_s= 0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this here from fig caption: We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are biased (the mode is $\sim 20 \%$ too high) due to the increasing inaccuracy of second-order SPT as we move into nonlinear scales}
\Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}
\\Another goal of this approach is to reproduce large scale structure in real space. To test this, we compute real space density fields by taking the inverse transform of both the directly measured long wavelength Fourier modes and the long wavelength modes predicted using the quadratic estimator. These density fields, $\delta$ and $\hat{\delta}$ respectively are plotted in Fig.~\rf{real}. We can see that \peikai{our quadratic estimator }
\RC{describe how well it works based on what we can see in the figure}
\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row). The bottom row shows their difference. Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.  The upper limit of $\vk_s$ is $0.22 \,h\, \rm Mpc^{-1}$.}

\noindent{\it Conclusion.}\label{sec4}
In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
\RC{ State that this is good because we won't be sensitive to observational systematics, sky gradients, dust etc}
\RC{Give a short list of cool things we can do, with references: measure 3D clustering beyond the matter radiation equality turnover for the first time, look for evidence of general relativistic effects which are strongest on large scales (e.g., \cite{Jeong:2012ls}), look for evidence of large scale anomalies, like in the CMB, constrain non-Gaussianity,  etc }\\
Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data. The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case. Thus, to detect even larger scales, we may need to use contributions from higher order perturbations and expand the integration range to reduce the noise level. \\
Another issue relates to the range of long-wavelength modes that are detectable. In the N-body simulation,  $k_l$ for modes recovered ranged from $2.5 \,h \times 10^{-3}  \rm Mpc^{-1}$ to $1.3\,h\times 10^{-2}  \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\ 
Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time. As the length scales are so large, a more realistic situation should deal with observations on the light cone. The expression for the quadratic estimator to be generalized to take this into account. Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshifts, in order to include more nonlinear information. Finally, when applied to datasets consisting of halos or galaxies, the approach should be modified to include galaxy bias. We also leave this to future work.\\

%\acknowledgements
\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu. The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).
